### 2020-04-18 README.Rmd

<!--
This specification assumes that incidence in a province ($y_st$) at time $t$ is partially determined by the weighted average ($Wy_{st}$) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period $\rho_t$ and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence ($\rho_i=\rho_j, \forall i,j$). The correspond Wald test is available in the `R` package `spsur`.
-->

This specification assumes that incidence in a province (![$y_st$](https://render.githubusercontent.com/render/math?math=%24y_st%24)) at time ![$t$](https://render.githubusercontent.com/render/math?math=%24t%24) is partially determined by the weighted average ![($Wy_{st}$)](https://render.githubusercontent.com/render/math?math=(%24Wy_%7Bst%7D%24)) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period ![$\rho_t$](https://render.githubusercontent.com/render/math?math=%24%5Crho_t%24) and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence (![$\rho_i=\rho_j, \forall i,j$](https://render.githubusercontent.com/render/math?math=%24%5Crho_i%3D%5Crho_j%2C%20%5Cforall%20i%2Cj%24)). The correspond Wald test is available in the `R` package `spsur`.

>>>>

<!--
This specification assumes that incidence in a province ($y_st$) at time $t$ is partially determined by the weighted average ($Wy_{st}$) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period $\lambda_t$ and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence ($\lambda_i=\lambda_j, \forall i,j$). The correspond Wald test is available in the `R` package `spsur`.
-->

This specification assumes that incidence in a province (![$y_st$](https://render.githubusercontent.com/render/math?math=%24y_st%24)) at time ![$t$](https://render.githubusercontent.com/render/math?math=%24t%24) is partially determined by the weighted average ![($Wy_{st}$)](https://render.githubusercontent.com/render/math?math=(%24Wy_%7Bst%7D%24)) of incidence in neighbouring provinces. Coefficients for the spatially lagged variable are estimated for each time period ![$\lambda_t$](https://render.githubusercontent.com/render/math?math=%24%5Clambda_t%24) and identifies the intensity and the sign of the impacts of neighbourhood. It is possible test the null hypotheis of identtical levels of spatial dependence (![$\lambda_i=\lambda_j, \forall i,j$](https://render.githubusercontent.com/render/math?math=%24%5Clambda_i%3D%5Clambda_j%2C%20%5Cforall%20i%2Cj%24)). The correspond Wald test is available in the `R` package `spsur`.
